---
title: "Kids Data"
author: "Angela Wang"
date: "October 10, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r load-packages, message=FALSE}
library(tidyverse)
library(readr)
library(broom)
library(knitr)
library(skimr)
library(ggpubr)
```

# Promis Peer 
```{r}
promispeer <- read_csv("Children PROMIS Peer.csv")
promispeer$`RawScore`<- as.numeric(promispeer$`RawScore`)
promispeer$`Gender`<- as.factor(promispeer$`Gender`)
```

```{r}
ggplot(data = promispeer, aes(x = `RawScore`)) + 
  geom_histogram( bins = 10, color = "black", fill = "gray") +
  labs(title = "Distribution of Promis Peer Scores for Children", x = "Total Score")

ggplot(data=promispeer, aes( x=`Gender`, y = `RawScore`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title="Relationship between Total Scores and Gender", y ="Total Score", x = "Gender")

ggplot(data=promispeer, aes( x=`New?`, y = `RawScore`, fill = `New?`)) + 
  geom_boxplot() +
  labs(title="Relationship between Total Scores and New Children", y ="Total Score", x = "New or not")

ggplot( data = promispeer, aes(x = `Age`, y =`RawScore` )) +
  geom_smooth() +
  labs(title = "Relationship between Total Scores and Age", x = "Age", y = "Total Score")
```

```{r}
t.test(promispeer$`RawScore` ~ promispeer$`Gender`, data = promispeer, var.equal = FALSE)
t.test(promispeer$`RawScore` ~ promispeer$`New?`, data = promispeer, var.equal = FALSE)
```

The p-value for the T-test comparing PROMIS peer scores between genders is above .05 indicating that there is not a significant difference between PROMIS scores between males and females.

The p-value for the T-test comparing PROMIS peer scores between new and returning children is above than .05 indicating that there is not a significant difference between PROMIS scores between new and returning children.

# Promis Family 
```{r}
promisfam <- read_csv("Children PROMIS Family.csv")
promisfam$`RawScore`<- as.numeric(promisfam$`RawScore`)
promisfam$`Gender`<- as.factor(promisfam$`Gender`)
```

```{r}
ggplot(data = promisfam, aes(x = `RawScore`)) + 
  geom_histogram( bins = 10, color = "black", fill = "gray") +
  labs(title = "Distribution of Promis Family Scores for Children", x = "Total Score")

ggplot(data=promisfam, aes( x=`Gender`, y = `RawScore`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title="Relationship between Total Scores and Gender", y ="Total Score", x = "Gender")

ggplot(data=promisfam, aes( x=`New?`, y = `RawScore`, fill = `New?`)) + 
  geom_boxplot() +
  labs(title="Relationship between Total Scores and New Children", y ="Total Score", x = "New or not")

ggplot( data = promisfam, aes(x = `Age`, y =`RawScore` )) +
  geom_smooth() +
  labs(title = "Relationship between Total Scores and Age", x = "Age", y = "Total Score")
```

```{r}
t.test(promisfam$`RawScore` ~ promisfam$`Gender`, data = promisfam, var.equal = FALSE)
t.test(promisfam$`RawScore` ~ promisfam$`New?`, data = promisfam, var.equal = FALSE)
```

The p-value for the T-test comparing PROMIS scores between genders is above .05 indicating that there is not a significant difference between PROMIS scores between males and females.

The p-value for the T-test comparing PROMIS scores between new and returning children is less than .05 indicating that there is a significant difference between PROMIS scores between new and returning children.
