---
title: "Social Worker Analysis"
author: "Angela Wang"
date: "August 7, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-packages, message=FALSE}
library(tidyverse)
library(readr)
library(broom)
library(knitr)
library(skimr)
```

# PHQ-9

```{r load-data-phq9}
phq9 <- read_csv("Social Workers PHQ-9 2020.csv")
phq9 <- as.tibble(phq9)
phq9<- phq9 %>%
  mutate(`Depression Severity` = fct_relevel(`Depression Severity`, levels = "Minimal depression", "Mild depression", "Moderate depression"))

view(phq9)
```

## Exploratory Graphs 
```{r graphs-phq9}

ggplot(data = phq9, aes(x = `Total: Used to see severity of depressive disorder`)) + 
  geom_histogram( bins = 10, color = "black", fill = "gray") +
  labs(title = "Depression Scores in Social Workers", x = "Total Depression Score")


ggplot(data = phq9, aes(x = `Depression Severity` )) + 
  geom_bar() +
  labs(title = "Frequency of Depression Severity in Social Workers", y = "Count")


ggplot(data=phq9, mapping = aes(fill= `Depression Severity`, x=`Gender`)) + 
  geom_bar(position="fill") +
  labs(title="Relationship between Depression Severity and Gender", y ="Proportion", x = "Gender", fill = "Depression Severity")


ggplot( data = phq9, aes(x = `Age`, y =  `Total: Used to see severity of depressive disorder` )) +
  geom_smooth() +
  labs(title = "Relationship between Total Depression Scores and Age", x = "Age", y = "Total Depression Score")

ggplot( data = phq9, aes( x = `Depression Severity`, y = `Age`, fill = `Gender`)) + 
  geom_boxplot() + 
  labs(title = "Relationship between Depression Severity and Age")


ggplot( data = phq9, aes(x = `Time in Ghar in Months`, y = `Total: Used to see severity of depressive disorder`)) +
  geom_smooth() +
  labs(title = "Relationship between Total Depression Scores and Time in Ghar", x = "Time in Ghar (months)", y = "Total Depression Score")

ggplot( data = phq9, aes( x = `Depression Severity`, y = `Time in Ghar in Months`, fill = `Gender`)) + 
  geom_boxplot() + 
  labs(title = "Relationship between Depression Severity and Time in Ghar", y = "Time in Ghar (months)")
```

## Mean/Median/Range of Total Depression Scores
```{r sum-scores-phq9 }
summary(phq9$`Total: Used to see severity of depressive disorder`)
```

## Standard Deviation of Total Depression Scores
```{r sd-phq9}
sd(phq9$`Total: Used to see severity of depressive disorder`)
```

# GAD-7
```{r load-data-gad7}
gad7 <- read_csv("Social Workers GAD-7 2020.csv")
gad7 <- as.tibble(gad7)
gad7 <- gad7[-c(12, 13,14,15,16,17,18,19,20,21,22), ]
view(gad7)
```

## Exploratory Graphs
```{r graphs-gad7}

ggplot(data = gad7, aes(x = `Total Score`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Anxiety Scores in Social Workers", x = "Total Anxiety Score", y = "Count")


ggplot(data = gad7, aes(x = `Anxiety Severity` )) + 
  geom_bar() +
  labs(title = "Frequency of Anxiety Severity in Social Workers", y = "Count")

ggplot(data= gad7, mapping = aes(fill= `Anxiety Severity`, x=`Gender`)) + 
  geom_bar(position="fill") +
  labs(title="Relationship between Anxiety Severity and Gender", y ="Proportion", x = "Gender", fill = "Anxiety Severity")


ggplot(data = gad7, aes(x = `Age`, y = `Total Score`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Total Anxiety Scores", x= "Age", y = "Total Anxiety Scores")

ggplot( data = gad7, aes( x = `Anxiety Severity`, y = `Age`, fill = `Gender`)) + 
  geom_boxplot() + 
  labs(title = "Relationship between Anxiety Severity and Age", y = "Age")


ggplot(data = gad7, aes(x = `Time in Ghar in Months`, y = `Total Score`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Total Anxiety Scores", x= "Time in Ghar (Months)", y = "Total Anxiety Scores")

ggplot( data = gad7, aes( x = `Anxiety Severity`, y = `Time in Ghar in Months`, fill = `Gender`)) + 
  geom_boxplot() + 
  labs(title = "Relationship between Anxiety Severity and Time in Ghar", y = "Time in Ghar (months)")
```

## Mean/Median/Range of Total Anxiety Scores
```{r sum-scores-gad7}
summary(gad7$`Total Score`)
```

## Standard Deviation of Total Anxiety Scores
```{r sd-gad7}
sd(gad7$`Total Score`)
```

# OBI

```{r load-data-OBI}
obi <- read_csv("Social Workers OBI 2020.csv")
obi <- obi[-c(12,13,14,15,16), ]
obi$`Average Burnout Score` <- (obi$`Overall Sum` / 16)
view(obi)
```

```{r graphs-obi}

ggplot(data = obi, aes(x = `Average Burnout Score`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Burnout Scores in Social Workers", x = "Average Burnout Score", y = "Count")

ggplot(data = obi, aes(x = `Disengagement Mean`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Disengagement Scores in Social Workers", x = "Average Disengagement Score", y = "Count")

ggplot(data = obi, aes(x = `Exhaustion Mean`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Exhaustion Scores in Social Workers", x = "Average Exhaustion Score", y = "Count")

ggplot(data = obi, aes(x = `Gender`, y = `Average Burnout Score`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Burnout Scores and Gender", x = "Average Burnout Score", y = "Gender", fill = "Gender")

ggplot(data = obi, aes(x = `Gender`, y = `Disengagement Mean`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Disengagement Scores and Gender", x = " Average Disengagement Scores", y = "Gender", fill = "Gender")

ggplot(data = obi, aes(x = `Gender`, y = `Exhaustion Mean`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Exhaustion Scores and Gender", x = " Average Exhaustion Scores", y = "Gender", fill = "Gender")

ggplot(data = obi, aes(x = `Age`, y = `Average Burnout Score`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Burnout Scores", x= "Age", y = "Average Burnout Scores")

ggplot(data = obi, aes(x = `Age`, y = `Disengagement Mean`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Disengagement Scores", x= "Age", y = "Average Disengagement Scores")

ggplot(data = obi, aes(x = `Age`, y = `Exhaustion Mean`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Exhaustion Scores", x= "Age", y = "Average Exhaustion Scores")

ggplot(data = obi, aes(x = `Time in Ghar`, y = `Average Burnout Score`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Average Burnout Scores", x= "Time in Ghar (months)", y = "Average Burnout Scores")

ggplot(data = obi, aes(x = `Time in Ghar`, y = `Disengagement Mean`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Average Disengagement Scores", x= "Time in Ghar(months)", y = "Average Disengagement Scores")

ggplot(data = obi, aes(x = `Time in Ghar`, y = `Exhaustion Mean`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Average Exhaustion Scores", x= "Time in Ghar (months)", y = "Average Exhaustion Scores")

```

## Mean/Median/Range of Average Burnout Scores
```{r sum-scores-obi}
summary(obi$`Average Burnout Score`)
```

## Standard Deviation of Average Burnout Scores
```{r sd-obi}
sd(obi$`Average Burnout Score`)
```

## Mean/Median/Range of Mean Disengagement Scores
```{r sum-dis-obi}
summary(obi$`Disengagement Mean`)
```

## Standard Deviation of Mean Disengagement Scores
```{r sd-dis-obi}
sd(obi$`Disengagement Mean`)
```

## Mean/Median/Range of Mean Exhaustion Scores
```{r sum-exh-obi}
summary(obi$`Exhaustion Mean`)
```

## Standard Deviation of Mean Exhaustion Scores
```{r sd-exh-obi}
sd(obi$`Exhaustion Mean`)
```

# MHC-SF
```{r load-data-mhc}
mhc <- read_csv("Social Workers MHC-SF 2020.csv")
mhc <- mhc[-c(12,13,14,15), ]
mhc$`Overall` <- as.numeric(mhc$`Overall`)
mhc$`Overall Average` <- (mhc$`Overall` / 14)

mhc$`EWB Average` <- as.numeric(mhc$`EWB Average`)
mhc$`PWB Average` <- as.numeric(mhc$`PWB Average`)
mhc$`SWB Average` <- as.numeric(mhc$`SWB Average`)

view(mhc)
```


```{r graphs-mhc}

ggplot(data = mhc, aes(x = `Overall Average`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Overall Wellbeing Scores in Social Workers", x = "Average Mental Wellbeing Score", y = "Count")

ggplot(data = mhc, aes(x = `EWB Average`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Emotional Wellbeing in Social Workers", x = "Average Emotional Wellbeing Score", y = "Count")

ggplot(data = mhc, aes(x = `SWB Average`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Social Wellbeing in Social Workers", x = "Average Social Wellbeing Score", y = "Count")

ggplot(data = mhc, aes(x = `PWB Average`)) + 
  geom_histogram(bins = 10,color = "black", fill = "gray") +
  labs(title = "Average Psychological Wellbeing in Social Workers", x = "Average Psychological Wellbeing Score", y = "Count")

ggplot(data = mhc, aes(x = `Gender`, y = `Overall Average`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Mental Wellbeing Scores and Gender", x = "Average Mental Wellbeing Score", y = "Gender", fill = "Gender")

ggplot(data = mhc, aes(x = `Gender`, y = `EWB Average`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Emotional Wellbeing and Gender", x = "Average Emotional Wellbeing Scores", y = "Gender", fill = "Gender")

ggplot(data = mhc, aes(x = `Gender`, y = `SWB Average`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Social Wellbeing and Gender", x = "Average Social Wellbeing Scores", y = "Gender", fill = "Gender")

ggplot(data = mhc, aes(x = `Gender`, y = `PWB Average`, fill = `Gender`)) + 
  geom_boxplot() +
  labs(title = "Relationship between Average Psychological Wellbeing and Gender", x = "Average Psychological Wellbeing Scores", y = "Gender", fill = "Gender")

ggplot(data = mhc, aes(x = `Age`, y = `Overall Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Mental Wellbeing", x= "Age", y = "Average Mental Wellbeing Scores")

ggplot(data = mhc, aes(x = `Age`, y = `EWB Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Emotional Wellbeing", x= "Age", y = "Average Emotional Wellbeing Scores")

ggplot(data = mhc, aes(x = `Age`, y = `SWB Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Social Wellbeing", x= "Age", y = "Average Social Wellbeing Scores")

ggplot(data = mhc, aes(x = `Age`, y = `PWB Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Age and Average Psychological Wellbeing", x= "Age", y = "Average Psychological Wellbeing Scores")

ggplot(data = mhc, aes(x = `Time in Ghar in Months`, y = `Overall Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Overall Mental Wellbeing", x= "Time in Ghar (months)", y = "Overall Mental Wellbeing Scores")

ggplot(data = mhc, aes(x = `Time in Ghar in Months`, y = `EWB Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Average Emotional Wellbeing", x= "Time in Ghar(months)", y = "Average Emotional Wellbeing Scores")

ggplot(data = mhc, aes(x = `Time in Ghar in Months`, y = `SWB Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Average Social Wellbeing", x= "Time in Ghar(months)", y = "Average Social Wellbeing Scores")

ggplot(data = mhc, aes(x = `Time in Ghar in Months`, y = `PWB Average`)) +
  geom_smooth() +
  labs(title = "Relationship between Time in Ghar and Average Psychological Wellbeing", x= "Time in Ghar(months)", y = "Average Psychological Wellbeing Scores")
```

## Mean/Median/Range of Average Mental Wellbeing Scores
```{r sum-scores-mhc}
summary(mhc$`Overall Average`)
```

## Standard Deviation of Average Burnout Scores
```{r sd-mhc}
sd(mhc$`Overall Average`)
```

## Mean/Median/Range of Average Emotional Wellbeing Scores
```{r sum-ewb-obi}
summary(mhc$`EWB Average`)
```

## Standard Deviation of Average Emotional Wellbeing Scores
```{r sd-ewb-obi}
sd(mhc$`EWB Average`)
```

## Mean/Median/Range of Average Social Wellbeing Scores
```{r sum-swb-obi}
summary(mhc$`SWB Average`)
```

## Standard Deviation of Average Social Wellbeing Scores
```{r sd-swb-obi}
sd(mhc$`SWB Average`)
```

## Mean/Median/Range of Average Psychological Wellbeing Scores
```{r sum-pwb-obi}
summary(mhc$`PWB Average`)
```

## Standard Deviation of Average Psychological Wellbeing Scores
```{r sd-pwb-obi}
sd(mhc$`PWB Average`)
```